---
title       : Car Trends
subtitle    : Predict Your Car Milage
author      : Sasidhar Donaparthi
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Objective

Objective of this presentation is provide to update on following after analyzing the The data was extracted from the 1974 _Motor Trend_ US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). 

* Exploratory Analysis
* Fit a Liner model to estimate the miles/(US) gallon
* Summary
    
### Data Points

<u>mpg</u> : Miles/(US) gallon,  <u>cyl</u> : Number of cylinders, <u>disp</u> : Displacement (cu.in.)
<br><u>hp</u> : Gross horsepower,<u>drat</u> : Rear axle ratio, <u>wt</u> : Weight (lb/1000)
<br><u>qsec</u> : 1/4 mile time,<u>vs</u> : V/S, <u>am</u> : Transmission (0 = automatic, 1 = manual)
<br><u>gear</u> : Number of forward gears, <u>carb</u> : Number of carburetors

---

## Exploratory Analysis
Follwing charts shows the relationship between various predictors and the outcome miles/(US) gallon

```{r echo=FALSE,results='asis',fig.width=10, fig.height=6.5}
data(mtcars)
mydata <- mtcars
par(mfrow=c(2,2))
plot(mtcars$wt,mtcars$mpg,xlab="Weight in 1000 lbs",ylab="miles/(US) gallon",pch=21,col="blue")
plot(mtcars$hp,mtcars$mpg,xlab="Gross Horse Power(hp)",ylab="miles/(US) gallon",pch=21,col="blue")
plot(mtcars$cyl,mtcars$mpg,xlab="Number of Cylinders",ylab="miles/(US) gallon",pch=21,col="blue")
plot(mtcars$disp,mtcars$mpg,xlab="Displacement (cu. in.)",ylab="miles/(US) gallon",pch=21,col="blue")
```

---

## Linear Model

We use number of cylenders, horse power, weight as the <em>predictors</em> and the <em>outcome</em> as miles/(US) gallon
```{r echo=FALSE, results='hide', eval=TRUE}
corcoef <- cor(mtcars$cyl,mtcars$disp)
```
Displacement has a strong relationship with number of cylinders, corelation coffecient = `r corcoef`
Let's consider # of clylinders instead of displacement.

Here is our model

```{r echo=FALSE, results='hide', eval=TRUE}
library(caret)
set.seed(12345)
intrain = createDataPartition(mydata$mpg,p=0.7,list=FALSE)
training = mydata[intrain,]
testing = mydata[-intrain,]
dim(training);dim(testing)
```
```{r echo=TRUE, results='hide', eval=TRUE}
modFit <- train(mpg ~ cyl + wt + hp + am, method="lm",data=training)
mpg_predict <- predict(modFit,newdata=testing)
```

---

## Summary

*  All of the predictors have negative relationship with miles/(US) gallon
*  Holdinng all other predictors constatnt, Automatic transmission is more effecient than manual transition

You can use <a href="http://sdonapar.shinyapps.io/myshinyapp">"Predict Your Car Milage"</a> for interactive application


```{r, echo=FALSE}

```

